{\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment

### 2020-08-15 documents/clinical_protocol.tex
Coplanar

\title{{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation}

@@

%\footnote{The}

This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}} A paltry few more details and a bibliography are available therein.

%\subfile{pulse_1.tex}

Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

Please distrust our analysis.

%The literature is littered with irreproducible claims of non-thermal effects; however, this appears to be a singular anomaly.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{../media/eppenwolf.jpg}
	\caption{Failure is just success rounded down.}
\end{figure}

\clearpage

@@

\cite{Efficient2015} specifically provides a reasonable spherical-cow model for how this could occur that agrees well with experiment.\footnote{See also \ghfile{documents/biology.ipynb}}

However, this work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.

Barring protein mechanical fatigue \cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales. This incidentally also permits scanning of a focal point so that a significant area can be treated with a relatively small transmit power.

@@

%\centering {\color{red} \faHeart}

\clearpage

@@

\printbibliography[heading=none, title={}]

>>>>

\title{ {\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment}

@@

@@

\cite{Efficient2015} specifically provides a reasonable "spherical-cow" model for how this could occur that agrees well with experiment.\footnote{See also \ghfile{documents/biology.ipynb}}

This work would seem to be more useful if extended with the following assertion: the virus' Q factor has been determined to be only about 2, meaning that the steady-state amplitude and stresses should be reached in some nanoseconds.

Barring protein mechanical fatigue\cite{Mechanical2013} or some other mechanism that could prolong the inactivation duration, it appears to be possible to reduce the required dissipated energy density to a minuscule fraction of all safety limits by pulsing the field at nanosecond scales. This incidentally also permits scanning of a focal point so that a significant area can be treated with a relatively small transmit power.

@@

@@

microwave diathermy and hyperthermia;

Several more recent papers \cite{Theoretical2020} on the technique have been published, but these are largely pseudoscientific and lack detail.

We are not aware of any clinical trial using microwave at these frequencies.

Research question: 
Does 
Null Hypothesis: There is no difference in fluoride release between the Compomer and Glass- ionomer cement.
Alternate Hypothesis: There is a difference in fluoride release between the Compomer and Glass-ionomer cement.
Disease progression

Proposed intervention:

\section{Potential Benefits and Risks to Patients:}

\section{Operational Planning and Budgeting:}

Keysight / Agilent 83732B
